\documentclass[a4paper,12pt]{article}
\usepackage{hyperref}
\usepackage{times}
\usepackage{comment}
\usepackage{titlesec}
\usepackage[pdftex]{graphicx}

\usepackage{geometry}
\geometry{lmargin=1.5cm,rmargin=1.5cm,height=25cm}
\renewcommand{\thesubsection}{\Roman{subsection}}

\begin{document}
\title{%LETTER TO THE EDITOR\\
  The langue of England on Vittoriosa}

\author{}
\date{}
\maketitle
\thispagestyle{empty}
\parskip\parindent

Sir, I would like to tell you about something that suddenly made me
sit up as I read the article ``The Langue of England in Vittoriosa''
by Lorenzo Zahra in the Easter 2004 issue of \textit{Treasures of
  Malta}.  It's a family matter that sadly reflects the attitudes of
its time.

The passage I refer to is on page 47 and reads as follows:
``\textit{In 1903 the bastion comprising the Post of England was
  almost completely demolished, ironically, by the British
  authorities.  The rubble was used for works on the breakwater arm at
  the mouth of the Grand Harbour which was under construction at the
  time and when completed in 1906 was inaugurated by King Edward VII.
  In the process the ancient underground Galley Slave Prison was
  obliterated when the site was excavated and converted into a tennis
  court!  It is now part of a development project."}

Well, I am pretty certain that the Philistine who pillaged this
historical site and converted it into a tennis court was my
grandfather, Sir Henry Pilkington.  The dates match, and I've always
understood that his engeering feats around the world included a
breakwater in the Valletta harbour; but the family seems to have taken
little interest in keeping records, letters, etc. (my mother only
remembered the crates of Malta oranges he used to have sent home).
And when in Malta myself I never got round to investigating the
archives.

I feel the author of the article has been extremely restrained to end
with just one exclamation mark.  I am curious about the ``development
project'' he mentions as under way now, but certainly it will be far
more worthy of the site --- times thankfully having changed so very much
for the better.

\vskip1cm

\leftline{Oxford\hfill JOANNA LACE}
\end{document}
